{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-02 bmvc_review.tex
Completed to do a proofreading on the experimental section.

\textbf{Performance on OTB100 Dataset.}  We evaluated the performance
of the {\it E}nKCF tracker on the OTB100 dataset, and observed a
performance similar to that of UAV123 data. Figure
\ref{fig:UAV123_OTB100_DATASET} shows the results on the OTB100
dataset. For the precision metric, {\it E}nKCF performed slightly
better than most of tracking algorithms in high-speed
trackers. Interestingly, it outperformed another correlation filter
based tracker, DSST, but performing $5\%$ behind of another low-speed
scale adaptive SAMF tracker.

As in UAV123 dataset, the {\it E}nKCF
performs exceptionally in handling the scale changes. It is ranked as
the third best tracker while being the second highest speed tracker
behind MOSSE. These numbers prove that {\it E}nKCF is not only a good
candidate for tracking on a UAV-based mobile platform but also mobile
platforms on smart phones.
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Precision_UAV123.pdf}}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_UAV123.pdf}}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Precision_OTB100.pdf}}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_OTB100.pdf}}\\
\end{tabular}
\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the UAV123 (a) and OTB100 (b) datasets.}
\label{fig:UAV123_OTB100_DATASET}
\end{figure}

>>>>

\textbf{Performance on OTB100 Dataset.}  We evaluated the performance
of the {\it E}nKCF tracker on the OTB100 dataset. Figure
\ref{fig:UAV123_OTB100_DATASET} shows the results on the OTB100
dataset. Like in UAV123 dataset, we observed a similar performance. In
particular, {\it E}nKCF showed a good performance for handling the
scale changes. It was the third best and the second fastest tracking
algorithm. For the precision metric, {\it E}nKCF performed slightly
better than most of tracking algorithms in high-speed
trackers. Interestingly, it outperformed another correlation filter
based tracker, DSST, but performing $5\%$ behind of another low-speed
scale adaptive SAMF tracker. 
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Precision_UAV123.pdf}}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_UAV123.pdf}}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Precision_OTB100.pdf}}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_OTB100.pdf}}\\
\end{tabular}
\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the UAV123 (a) and OTB100 (b) datasets.}
\label{fig:UAV123_OTB100_DATASET}
\end{figure}
